My title

### 2024-10-31 paper/paper.qmd
Upload for scripts
update the scripts files, delete unused files. Update the code inside all the files.

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

@@

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

>>>>

```{r}
#| include: false
#| warning: true
#| message: false

library(tidyverse)
library(modelsummary)
library(palmerpenguins)
library(ggplot2)
library(arrow)
library(here)
library(modelr)
library(rstanarm)
```

@@

```{r}
echo=TRUE
library(rstanarm)

if (file.exists(here::here("models/model_date.rds"))) {
  message("model_date.rds found.")
} else {
  message("model_date.rds not found.")
}

if (file.exists(here::here("models/model_date_pollster.rds"))) {
  message("model_date_pollster.rds found.")
} else {
  message("model_date_pollster.rds not found.")
}

```

@@

```{r}
modelsummary(models = list("Model 1" = model_date, "Model 2" = model_date_pollster))

```
